---
title: "R Libraries and Functions"
output: html_document
date: "2022-10-17"
---
**Base R**

```{r Base R functions}
#data.frame
#with()
#for()
 
```

**Dplyr**
[https://dplyr.tidyverse.org/articles/dplyr.html]

The functions in dplyr are the common "verbs" you use in data manipulations.
This example uses a dataset called starwars that is built into R for demonstration purposes
```{r Dplyr functions}
# Install packages once
#install.packages("dplyr")
library("dplyr")

# Look at starwars tibble

dim(starwars)
starwars

# The pipe: all dplyr functions take a data frame or tibble as the first argument. For efficiency, you can nest functions. The result from one step is piped to the next. You can read top-to-bottom, using %>% as "then"
# In Rstudio, the keyboard shortcut for the pipe operator %>% is Ctrl + Shift + M (Windows) or Cmd + Shift + M (Mac)

# functions used in class:

# filter is used to choose rows based on column values
# filter the starwars tibble for female characters with brown eyes
# note that we need to use == to select the variables
# filter selects rows where the expression is TRUE

starwars %>%
  filter(sex == "female", eye_color == "brown")

# mutate is used to add new columns that are functions of existing columns
# use mutate to create a new column for height in meters (in the existing dataset it is in cm)
# by default the new column is added at the end of the dataframe

starwars %>%
  mutate(height_m = height / 100)

# group_by is used to run a data operation on a group defined by variables. It is very useful in ggplot and in creating summaries
# use group_by to summarise the mean height and mass, grouped by species and sex

starwars %>%
  group_by(species, sex) %>%
  summarise(
    height = mean(height, na.rm = TRUE),
    mass = mean(mass, na.rm = TRUE)
  )

# count is used to count observations by group. You do not have to use the group by function.
# count the number of individuals of each species in the starwars dataset

starwars %>% count(species)

#slice_max
#left_join
#anti-join
```

**Package: Polite**
Developed by Dmytro Perepolkin
[https://dmi3kno.github.io/polite/]

Polite promotes good web etiquette during webscraping sessions.
It includes two main functions "bow" and "scrape".
Bow introduces the client to the host and asks for permission to scrape (it checks the robots.txt file).
Scrape is the main function for retrieving the data.

```{r Polite examples}
# Install packages once
#install.packages("polite")
library("polite")

# Examples of functions used in class, using cheese.com from package vignettes:

# bow asks for permission to scrape (it checks the robots.txt file)
host <- "https://www.cheese.com"
session <- bow(host)
session
# Output indicates if the path is scrapable.

# scrape follows bow. To scrape part of a website, you need to be able to identify and request sections of the website that match a css selector or Xpath expression using html_elements
# session was defined in bow, above
# To look at the website, ctrl+click and View page source or look at the developer view, depending on your browser. Selector Gadget can be helpful.

result <- scrape(session, query=list(t="semi-soft", per_page=100)) %>%
  html_node("#main-body") %>%
  html_nodes("h3") %>%
  html_text()
head(result)

# once you have scraped the data, create a new code chunk and do not run the request repeatedly. You may want to save the result to a file to work on it in another session, using write.csv
```

**Package: rvest**
Developed by Hadley Wickham
[https://rvest.tidyverse.org/]

rvest is used for scraping (or harvesting) data from web pages.
rvest is part of the tidyverse, but it can be installed separately

```{r rvest examples}
# Install packages once
#install.packages("tidyverse")
library("tidyverse")
# or, can install rvest separately
#install.packages("rvest")
library("rvest")

# Examples of functions used in class, using Star Wars example from vignette:

# read_html is from the xml2 package. You can add encodings, which we didn't do in this class. In rvest, it is used to read/scrape the html document.

starwars <- read_html("https://rvest.tidyverse.org/articles/starwars.html")

# html_element and html_elements find HTML element(s) using CSS selectors or XPath expressions. Particularly useful in conjunction with SelectorGadget

films <- starwars %>%
  html_elements("section")
films

# html_element will find only the first element of that type. Compare films (above) and film (below)

film <- starwars %>%  
  html_element("section")
film

# html_text2 retrieves text from an html element. html_text2 simulates how text looks in a browser. Look at title below and titleNoMarkup

title <- films %>%
  html_elements("h2")
title

titleNoMarkup <- films %>%
  html_elements("h2") %>%
  html_text2()
titleNoMarkup

```

**Package: gutenbergr**

```{r Gutenbergr}
#install.packages("devtools")
library("devtools")
#devtools::install_github("ropensci/gutenbergr")
library("gutenbergr")

#gutenberg_works
#gutenberg_download
```

**Package: tidytext**

```{r Tidytext functions}
#stop_words
#get_sentiments
```