---
title: "Web Scraping: Genius Example and Lab"
output: html_notebook
---
**Shortcuts and reminders**

%>% (pipe operator) is Ctrl+Shift+M (Windows) or Cmd+Shift+M (Mac).

<- (assignment operator) is Alt + - (Windows) or Option + - (Mac).

run a line of code from the source editor use Ctrl+Enter (Windows) or Cmd+Enter (Mac)

tab to autocomplete long variable names

**Scraping song lyrics from Genius.com**
```{r install packages}
#Install packages once
#install.packages("tidyverse")
#install.packages("dplyr")
#install.packages("rvest")
#install.packages("polite")
#install.packages("tidytext")
#install.packages("textdata")
#install.packages("geniusr")

library("tidyverse")
library("dplyr")
library("rvest")
library("polite")
library("tidytext")
library("textdata")
library("geniusr")
```

Use bow function from Polite to see if we can scrape a site
```{r bow to Genius}
GeniusSession <- bow("https://genius.com/artists/Julie-doiron")
GeniusSession
```

Check for an API and R package
geniusr: https://ewenme.github.io/geniusr/
API: https://docs.genius.com/

Lab:
Choose a different artist
Following Web Scraping Part 1 Dracula example,
- tokenize the lyrics
- remove stop words
- analyze using nrc lexicon
- use ggplot to create a sentiment analysis plot
- give the plot a title including the artist's name
- export the plot
- add it to your GitHub repo

```{r set up genius token}
genius_token()
```

**Example: Julie Doiron**
```{r identify artist and scrape lyrics}
Artist <- "Julie Doiron"

GetArtistInfo <- search_artist(search_term = Artist)

ArtistSongs <- get_artist_songs_df(GetArtistInfo$artist_id)
head(ArtistSongs)
```

Get Lyrics
```{r get lyrics}
#Approach 1
#lyrics <- data_frame()
#for (i in 1:(nrow(ArtistSongs))) {
#  songlyrics <- get_lyrics_id(ArtistSongs$song_id[i])
#  lyrics <- rbind(lyrics, songlyrics)
#  i + 1
#}

#Approach 2
#https://www.r-bloggers.com/2021/01/scraping-analysing-and-visualising-lyrics-in-r/
#Use a tryCatch function / Question: would the function "possibly" work? That is what Doug has used.

ids <- c(as.character(ArtistSongs$song_id))
allLyrics <- data.frame()

while (length(ids) > 0) {
  for (id in ids) {
    tryCatch({
      allLyrics <- rbind(get_lyrics_id(id), allLyrics)
      successful <- unique(allLyrics$song_id)
      ids <- ids[!ids %in% successful]
      print(paste("done - ", id))
      print(paste("New length is ", length(ids)))
    }, error = function(e){})
  }
}

head(allLyrics)