---
title: "Web Scraping: Genius Lab Setup"
output: html_notebook
---
**Shortcuts and reminders**

%>% (pipe operator) is Ctrl+Shift+M (Windows) or Cmd+Shift+M (Mac).

<- (assignment operator) is Alt + - (Windows) or Option + - (Mac).

run a line of code from the source editor use Ctrl+Enter (Windows) or Cmd+Enter (Mac)

tab to autocomplete long variable names

**Scraping song lyrics from Genius.com**
```{r install packages}
#Install packages in console if necessary
#install.packages("tidyverse")
#install.packages("dplyr")
#install.packages("rvest")
#install.packages("polite")
#install.packages("tidytext")
#install.packages("textdata")
#install.packages("devtools")

library("tidyverse")
library("dplyr")
library("rvest")
library("polite")
library("tidytext")
library("textdata")
library("devtools")
```

Use bow function from Polite to see if we can scrape a site
```{r bow to Genius page for your chosen artist}
GeniusSession <- bow("https://genius.com/artists/Janelle-monae")
GeniusSession
```

Check for an API and R package.
There is a geniusr package developed by ewenme
geniusr: https://ewenme.github.io/geniusr/
However, there is an error in retrieving lyrics. Take a look at the issue called "error with "getlyrics_id()"
We will instead load the version of geniusr forked by giovanni-cutri, using devtools to load his version from github.

Additional setup:
Create an account on Genius.com
Go to genius.com/developers and Create an API Client
Give your app a name in the format Data3101TestYourInitials
Give your app a app website URL in the format https://github.com/MtADATA3101/lastname_firstname 

You will need to copy the client access token to complete this exercise.

Lab:
Choose a different artist
Follow steps in this file to get song lyrics for your chosen artist
Following Web Scraping Frankenstein example,
- tokenize the lyrics
- remove stop words
- analyze using nrc lexicon
- use ggplot to create a sentiment analysis plot
- give the plot a title including the artist's name
- export the plot
- add it to your GitHub repo

Help for ggplot function (adding a title):
Look at the ggplot2 cheatsheet available through Posit: https://posit.co/resources/cheatsheets/
https://rstudio.github.io/cheatsheets/html/data-visualization.html?_gl=1*iv665*_ga*MTYzNDc4Nzk2Ny4xNjkxODg2NzQw*_ga_2C0WZ1JHG0*MTcwMDE0NzExMy4xMi4wLjE3MDAxNDcxMTMuMC4wLjA.#basics

In the command line, run the following line of code:
devtools::install_github("giovanni-cutri/geniusr")

```{r set up genius token}
library("geniusr")
genius_token()
```

**Example: Janelle Monae**
```{r identify artist and scrape lyrics}
artist <- "Janelle Monae"

artist_info <- search_artist(search_term = artist)

artist_songs <- get_artist_songs_df(783)
# If this line fails because there is more than one artist id for your group, look in the artist_info dataframe for the most likely id. Replace artist_info$artist_id with the id number.
head(artist_songs)
```

Get Lyrics
```{r get lyrics}
#Approach 1: My attempt at creating a dataframe
#lyrics <- data_frame()
#for (i in 1:(nrow(artist_songs))) {
#  songlyrics <- get_lyrics_id(artist_songs$song_id[i])
#  lyrics <- rbind(lyrics, songlyrics)
#  i + 1
#}

#Approach 2
#https://www.r-bloggers.com/2021/01/scraping-analysing-and-visualising-lyrics-in-r/
#Use a tryCatch function / Question: would the function "possibly" work? That is what Doug has used.

ids <- c(as.character(artist_songs$song_id))
lyrics <- data.frame()

while (length(ids) > 0) {
  for (id in ids) {
    tryCatch({
      lyrics <- rbind(get_lyrics_id(id), lyrics)
      successful <- unique(lyrics$song_id)
      ids <- ids[!ids %in% successful]
      print(paste("done - ", id))
      print(paste("New length is ", length(ids)))
    }, error = function(e){})
  }
}

head(lyrics)
```